%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{paratype}
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Georgy} % Your first name
\familyname{Lukyanov} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{44 Pushkinskaya st.}{344082 Rostov-on-Don, Russia}
\mobile{+7(908) 506 9512}
\email{georgiy.lukjanov@gmail.com}
\homepage{geo2a.github.io}{geo2a.github.io} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
% \extrainfo{additional information}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

% Colored hyperlinks
\newcommand\Colorhref[3][cyan]{\href{#2}{\small\color{#1}#3}}

%----------------------------------------------------------------------------------------

\begin{document}

% %----------------------------------------------------------------------------------------
% %	COVER LETTER
% %----------------------------------------------------------------------------------------

% % To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-2] % Dummy text
% \lipsum[4] % Dummy text

% \makeletterclosing % Print letter signature

\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2015--2017 (in-progress)}{M. Sc. in Computer Science}{Southern Federal University, I. I. Vorovich Institute of Mathematics, Mechanics and Computer Science}{Rostov-on-Don, Russia}{}{}  % Arguments not required can be left empty
\cventry{February --\\June 2016}{Eramus+ exchange program}{Vilnius University, Faculty of Mathematics and Informatics, Faculty of Philology}{Vilnius, Lithuania}{}{}

\cventry{2011--2015}{B. Sc. in Applied Mathematics and Computer Science}{Southern Federal University, I. I. Vorovich Institute of Mathematics, Mechanics and Computer Science}{Rostov-on-Don, Russia}{}{}

\subsection{Selected courses taken}

\begin{itemize}
  \item Quantum Computing (Southern Federal University, 2016)
  \item Optimizing Compilers Development (Southern Federal University, 2016)
  \item Cryptography (Vilnius University, 2016)
  \item Insights into Academic Discourse (Vilnius University, 2016)
  \item Certified Software Development with Dependent Types in Idris (Southern Federal University, 2014)
  \item Machine Learning (Southern Federal University, 2015)
  \item FPGA programming (Southern Federal University, 2015)
  \item Functional Programming in Haskell (Southern Federal University, 2014)
  \item Supercomputer Technologies (Southern Federal University, 2014)
  \item Computer Organization (Southern Federal University, 2012)
\end{itemize}

%-------------------------------------------------------------------------------
% RESEARCH INTERESTS SECTION
%-------------------------------------------------------------------------------

\section{Research interests}

\begin{itemize}
  \item Functional programming
  \item Theory of programming languages
  \item Effectful programming
  \item Software development with typed functional languages
  \item Machine learning
\end{itemize}

\section{Master's thesis (work-in-progress)}

\cvitem{Working title}{\emph{``Student's Big Brother''}}
\cvitem{Supervisors}{Assistant Professor Artem Pelenitsyn}

\cvitem{Description}{
Distributed system to support study workflow in programming class.
It's created to help teacher to uniformly distribute his/her attention
between all students. System consists of client daemons, watching students
activity and sending their source code to server (over HTTP), for storage,
processing and displaying in teacher web-interface.
Source code is available on \Colorhref{https://github.com/geo2a/students-big-brother}{GitHub}.
}
\cvitem{Technology stack}{Haskell (servant), PostgreSQL, Javascript (Ember.js), Git.}

\section{Bachelor's thesis}

\cvitem{Title}{\emph{Functional parser of lightweight Markdown markup language based on monad combining and monoidal source stream representation}}
\cvitem{Supervisors}{Assistant Professor Artem Pelenitsyn}
\cvitem{Description}{
Parser-combinator library based on monad transformers and monoid-subclasses as a
representation of input stream was developed. This library was used to build
a lightweight tool for taking lecture notes: parsing Markdown with \LaTeX pieces
and rendering to HTML. Source code of library and tool is available on
\Colorhref{https://github.com/geo2a/markdown-monparsing}{GitHub}. A prototype of monadic parser-combinators library based on extensible effects
was built. Sources also are available on \Colorhref{https://github.com/geo2a/ext-effects-parsers}{GitHub}.
}

%-------------------------------------------------------------------------------
% TAKEN COURCES SECTION
%-------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{2015--Present}{Software Engineer}{\textsc{Statzilla}}{Rostov-on-Don}{}{
Taking part in projects connected with machine learning, statistics and digital
signal processing. Development of web and desktop applications.
\newline{}\newline{}
Detailed activities:
\begin{enumerate}
\item Development of statistical analysis web-service (R, C++, JavaScropt, PHP).
\item Organization of workflow of software development team:
  \begin{itemize}
    \item Version control (Git, Gitlab)
    \item Continuous integration (Gitlab CI)
  \end{itemize}
\item Organization of deployment procedures.
\item Development of computational back-end HTTP-service based on
\Colorhref{https://www.opencpu.org/}{Opencpu}.
\item Implementation of Windows desktop app for infant heart rate analysis based on digital
signal processing methods (R, C\#).
\item Solving various machine learning tasks: prediction of age of subscribers
of cellular provider based on data about services they are using, categorizing
crimes based on location on city map and some others.
\end{enumerate}
}

%------------------------------------------------

\cventry{Summer 2015}{Summer Intern}{\textsc{Statzilla}}{Rostov-on-Don}{}{}

%------------------------------------------------

\cventry{September--December 2015}{Teaching assistant}{\textsc{Southern Federal University}}{Rostov-on-Don}{}{
Teaching ``Functional Programming in Haskell'' labs with occasional lecturing.
}

%------------------------------------------------

\cventry{May--December 2014}{C\# Developer}{\textsc{Strob}}{Rostov-on-Don}{}{
Taking part in development of distributed system for collecting and processing
of water meter data. Development of SCADA-like .NET-application.
}

%-------------------------------------------------------------------------------
% CONFERENCES, etc.
%-------------------------------------------------------------------------------

\section{Awards}

\cvitem{December 2015}{First place in data analysis competition ``Me and the
World in 2030'' organized by bank Centr-Invest}

\cvitem{November 2015}{Third place in hackathon ``47 hours'' as a part of team
Statzilla for web-based arcade game project}

\cvitem{April 2015}{First place in students research competition "Week of Science 2015"
of Southern Federal University
with project ``Functional parser of lightweight Markdown markup language based on monad
combining and monoidal source stream representation''}

%-------------------------------------------------------------------------------
% COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{Computer skills}

  {\large \textbf{Programming languages}} \\
    % \begin{subsection}
      \emph{Strong knowledge}: Haskell, C\#, R, JavaScript, SQL \\
      \emph{Some experience}: C, C++, Java, PHP, Bash, Assembly, Idris
    % \end{subsection}

  {\large \textbf{Markup Languages}} \\
  HTML, CSS, \LaTeX, Markdown

  {\large \textbf{Other}} \\
  \emph{Virtualization}: VirtualBox, Vagrant, Docker \\
  \emph{Operating Systems}: GNU/Linux (Ubuntu) administration,
                            programming with Win32 API \\
  \emph{Version control}: Git
%-------------------------------------------------------------------------------
\section{General skills}

  {\large \textbf{Spoken languages}} \\
    % \begin{subsection}
      \emph{English}: C1 according to CEFR, IELST overall band score: 8.0 \\
      \emph{Russian}: native
    % \end{subsection}
%-------------------------------------------------------------------------------
% CULTURAL AND SOCIAL LIFE SECTION
%-------------------------------------------------------------------------------
\section{Cultural and social activities}

\cventry{2012--2014}{Performer}{Southern Federal University}{Rostov-on-Don}{}{
Various cultural activities, being part of creative team of Institute of Mechanics,
Mathematics and Computer Science.
\begin{itemize}
  \item Playing on stage as a part of the performance troupe called ``The Fashion Drama''.
  \item Helping freshmans to get into flow of cultural life of university.
  \item Being a part of stage service team.
\end{itemize}
}

\subsection{Awards}

\cvitem{2013-2015}{Multiple prizes of region-wide creative festival ``Russian Students Spring'' for performances. As a part of performance troupe
``The Fashion Drama''.
}

%----------------------------------------------------------------------------------------
% INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

% \renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvitem{Photography}{
Mainly landscape and conceptual. Some photos are available on \href{https://www.flickr.com/photos/113494852@N02/}{Flickr} and \href{https://www.facebook.com/georgiyl/photos_all}{Facebook}
}

\cvitem{Literature}{
  Albert Camus, John Fowles, Stanislaw Lem, Arkady and Boris Strugatsky
}

\cvitem{Sports}{Cycling, Swimming}

\end{document}
